Turbulence in compact to giant H~II regions

### 2023-04-16 strucfunc_paper.tex
Rewrite description of projection of simulated maps

\textcolor{red}{Then we proceed to create a 2D map from collapsing the 3D velocity field so we can take account of projection effects.
We do this by obtaining the 1st-moment map of a PPV (position-position velocity) cube created using the \texttt{make\textunderscore{}ppv} command from \texttt{turbustat}.
To create the PPV cube it was also necessary to create a 3D density field.
The same \texttt{make\textunderscore{}3dfield} command was used to create  (along with the same parameters of the velocity field) a fluctuating density field.
The density fluctuations are interpreted as emissivity fluctuations following as mentioned in section~\ref{sec:constancy-power-law}.}

@@

\textcolor{red}{Figure~\ref{fig:seeing-reduction}a} illustrates how four different
synthetic \textcolor{red}{1st-moment maps of} size \(256\times256\) pixels
and correlation length \textcolor{red}{\(r_0 = \SI{32}{pixels}\)}
are affected by progressively broader gaussian seeing,
with RMS width \(s_0 = 1\) to \SI{32}{pixels}.
We calculate the structure function \(B(r)\) for each map and show
in Figure~\ref{fig:seeing-reduction}b the average ratio between
\(B(r)\) and the value in the absence of seeing,
with different colors representing different values of \(s_0\).
Results are shown for a power-law slope of \textcolor{red}{\(m = 1.0\)}
but we find very similar behaviour for other values of \(m\) within the range
seen in our observations.
For small values of \(s_0\), the principle effect is seen at
the smallest separations but the structure function is noticeably depressed
for separations as large as \(r = 10 s_0\).
As \(s_0\) increases to become comparable with \(r_0\),
even the largest separations are significantly affected.
At the same time the apparent correlation length begins to increase,
as indicated by the plus symbols in the figure.

>>>>

{\color{red}%
  In order to create 2D plane-of-sky velocity map, we first
  create 3D cubes of fluctuating velocity and emissivity
  with \texttt{make\textunderscore{}3dfield},
  then transform to a PPV (position-position velocity) cube
  using the \texttt{make\textunderscore{}ppv} command from \texttt{turbustat},
  assuming thermal broadening with FWHM of \SI{20}{\kilo\meter\per\second},
  as appropriate for a hydrogen line at \(T \approx \SI{e4}{K}\).
  Finally, the first velocity moment map is obtained
  by integrating along the velocity axis.

  For the emissivity field, we assume a log-normal distribution
  with RMS fractional width
  \(\shortsig{E} = 1.0\) that is typical of our sources
  (see footnote~\ref{fn:brightness-fluctuations} and Figure~\ref{fig:brightness-pdfs} above).
  We further assume that there is no correlation between the emissivity
  and velocity fluctuations and that their spatial correlation length
  and power law indices are equal.\footnote{%
    We have investigated departures from these assumptions and found that they
    make very little difference to the results.
  }
}

@@

\textcolor{red}{Figure~\ref{fig:seeing-reduction}a} illustrates how four different
synthetic \textcolor{red}{1st-moment maps of} size \(256\times256\) pixels
and correlation length \textcolor{red}{\(r_0 = \SI{32}{pixels}\)}
are affected by progressively broader gaussian seeing,
with RMS width \(s_0 = 1\) to \SI{32}{pixels}.
\textcolor{red}{%
  Note that the seeing is applied to each velocity channel of the
  PPV emissivity cube before integrating to find the 2D velocity map.
}
We calculate the structure function \(B(r)\) for each map and show
in Figure~\ref{fig:seeing-reduction}b the average ratio between
\(B(r)\) and the value in the absence of seeing,
with different colors representing different values of \(s_0\).
Results are shown for a power-law slope of \textcolor{red}{\(m = 1.0\)}
but we find very similar behaviour for other values of \(m\) within the range
seen in our observations.
For small values of \(s_0\), the principle effect is seen at
the smallest separations but the structure function is noticeably depressed
for separations as large as \(r = 10 s_0\).
As \(s_0\) increases to become comparable with \(r_0\),
even the largest separations are significantly affected.
At the same time the apparent correlation length begins to increase,
as indicated by the plus symbols in the figure.
